
\section{About}

LOADays is the event for technologists interested in adopting, improving, and using Open Source operation software.\\
\par

The first LOADays was held in 2010 and has grown to more then 150 attendees.\\
The event is organized for system adminstrators and system operators.\\
We have the privilege to use the venue of the Don Bosco Wilrijk.\\
\par

This year LOADays takes places on \textbf{\confdates} in Wilrijk, Antwerp, Belgium.
\par

\section{Sponsorship}

LOADays is a free event, we aim to be a place for learning and working together around system administration and system operation.
\par

We offer an array of sponsor opportunities that fit a wide choice of options.\\
If the standard sponsor options do not fit your needs, please contact us to discuss any flexible sponsor options.
\par

When choosing your prefered sponsor budget, please keep in mind that we aim to keep the event FREE.\\
We provide breakfast, lunch, and coffee during the breaks to all attendants and a social event on Saturday evening.\\
Budget permitting we hold a speakers' dinner and offer t-shirts and/or other swag to attendees.
\par

\input{levels.tex}

\begin{itemize}
\item
Limit : This indicates the maximum number of sponsors in that level.
\item
Invoice : We provide an invoice from a Belgian company, please provide us with a valid EU VAT number or an export address.
\item
Website : Your logo is mentioned on the website \url{https://loadays.org/} .
\item
Shared table goodies : You have access to put company sponsored swag on a shared table.
\item
Speakers' dinner invite : if budget permits, we organize a speakers' dinner on Sunday in Ghent Centre, you, as a sponsor get an invite.
\item
Sponsor pitch : As a sponsor you will be permitted to do a Ignite talk with a commercial touch. We recommend all sponsors keep it as technical commercial.
\item
Streaming logo : If budget and resources permit, we will stream or record the event, your logo as a sponsor will be added here.
\end{itemize}

\section{Team}

\input{people.tex}

